---
title: "Using MMAPPR2data Resources"
author:
- name: Kyle Johnsen
  affiliation: Brigham Young University, Provo, UT
package: MMAPPR2data
output: 
  BiocStyle::html_document: default
  BiocStyle::pdf_document: default
abstract: |
  Instructions on loading BAM files and indices in MMAPPR2data package.
vignette: |
  %\VignetteIndexEntry{Using MMAPPR2data Resources}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}  
---

*******************************************************

We first load the `MMAPPR2data` package:

```{r}
library(MMAPPR2data, quietly = TRUE)
```

This package contains the following two functions, which
provide easy access to the BAM files and their indices,
returning `BamFile` objects:

```{r}
zy13wtBam()
zy13mutBam()
```

Or we can access the four raw files using the *ExperimentHub* interface:

```{r}
library(ExperimentHub)
eh <- ExperimentHub()
wtfiles <- listResources(eh, "MMAPPR2data", "wt")
wtfiles[[1]]        ## load the first resource in the list
## load all mutant files:
mutfiles <- loadResources(eh, "MMAPPR2data", "mut")
```

For details on the source of these files, and on their construction
see `?MMAPPR2data` and the scripts:

* `inst/scripts/make-metadata.R`
* `inst/scripts/make-data.sh`

```{r sessionInfo}
sessionInfo()
```

Thanks to Mike Love's `r Biocpkg("alpineData")` package for vignette structure inspiration.
